Total Platform Cyber Protection

### 2016-06-25 paper.tex
fix(biblio): removed duplicates and updated references to be consistent

Rootkits attempt to persist the attacker's compromise of the operating
system and allow them to hide their malicious behavior from other
applications on the system. Therefore, rootkit detection is an
important research topic in Operating System
security~\cite{Petroni2004, Wang2005, Petroni2007, Payne2008,
  Sharif2009, Yin2010, Bianchi2012}. Another approach is to prevent
the rootkit from altering the Operating System
kernel~\cite{Riley2008a, Wang2009, Grace2010, Gadaleta2011}.

@@

There has been significant research in the area of analysis of an application. Dynamic analysis~\cite{ball1999concept} analyzes the code at run time, and much research in this area has been into Taint-based tracking~\cite{Chang2008}, Anomaly Detection~\cite{Cova2007, li11:BLOCK, Li2012}, Context-sensitive sanitization for popular languages and templating languages~\cite{Saxena2011, Samuel2011}, and Binary Analysis~\cite{Song2008}. Other work has looked at automated attack generation using model checking~\cite{martin08:goal_directed_mc}, and classifying the available countermeasures for the C and C++ languages~\cite{Younan2012}.

>>>>

Rootkits attempt to persist the attacker's compromise of the operating
system and allow them to hide their malicious behavior from other
applications on the system. Therefore, rootkit detection is an
important research topic in Operating System
security~\cite{Petroni2004, Wang2005, Petroni2007, Payne2008,
  Sharif2009, Yin2010, Bianchi2012}. Another approach is to prevent
the rootkit from altering the Operating System
kernel~\cite{Riley2008, Wang2009, Grace2010, Gadaleta2011}.

@@

There has been significant research in the area of analysis of an application. Dynamic analysis~\cite{ball1999concept} analyzes the code at run time, and much research in this area has been into Taint-based tracking~\cite{Chang2008}, Anomaly Detection~\cite{Cova2007, li11:BLOCK, Li2012}, Context-sensitive sanitization for popular languages and templating languages~\cite{Saxena2011, Samuel2011}, Binary Analysis~\cite{Song2008}, and Logic vulnerabilities~{\cite{felmetsger10:logic}}. Other work has looked at automated attack generation using model checking~\cite{martin08:goal_directed_mc}, and classifying the available countermeasures for the C and C++ languages~\cite{Younan2012}.
